\textls[-0]{\thetitle}

### 2023-03-18 metatheory2.tex
Fixing typo. Adding ref.

\noindentparagraph{Explicit Universe Level.} Our treatment of universe level mainly follows that of \citet{altkap2016, kaposi2019gluing}. Universe level is mainly to get around the size issue---we cannot refer to(and thus quantifiy over) a set of all set (or a universe of all type). So everytime we want to quantify over a universe of types, we have to specify ``how large'' that universe is, that is basically what universe level is measuring.

Now we will need to some attach syntax pieces with natural number indicating universe level. The explicit universe level $i$ now will attach to each context and type judgement $\goodCtx{\Gm}{i}$ and $\goodType{\Gm}{T}{i}$ basically indicating the context $\Gm$ and $T$ inhabits at what universe. Apparently, universe level will also be attached to $\cU$. For two universe level $i,j$ (as natural number), we use $i \lcup j$ to denotes $\max(i,j)$.

>>>>

\noindentparagraph{Explicit Universe Level.} Our treatment of universe level mainly follows that of \citet{altkap2016, kaposi2019gluing}. Universe level is mainly to get around the size issue---we cannot refer to (and thus quantifiy over) a set of all set (or a universe of all type)~\cite{hurkens1995simplification}. So everytime we want to quantify over a universe of types, we have to specify ``how large'' that universe is, that is basically what universe level is measuring.

Now we will need to attach some syntax pieces with natural number indicating universe levels. The explicit universe level $i$ now will attach to each context and type judgement $\goodCtx{\Gm}{i}$ and $\goodType{\Gm}{T}{i}$ basically indicating the context $\Gm$ and $T$ inhabits at what universe. Apparently, universe level will also be attached to $\cU$. For two universe level $i,j$ (as natural number), we use $i \lcup j$ to denotes $\max(i,j)$.
